---
title: "Portfolio Analytics Report"
author: "Analyst: Muideen Abubakar"
date: "Date: `r Sys.Date()`"
output: 
  html_document:
    df_print: paged 
    number_sections: no
    theme: simplex
    highlight: kate
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
params:
  TraderID: DGR1983
  TradeDate: 2021-11-12
  InceptionDate: 2020-01-06
---

### Introduction

Sequel to the request from the front office, this report seeks to analyse the portfolio of trader **`r params$TraderID`** and generate a report on their portfolio. The report will convey the details of the main allocations and historical trends, particularly for the end of day allocation on **`r params$TradeDate`**. In addition, the report will indicate the performance and risk metrics for this trader's portfolio via tables and charts which will aid the front office to monitor the trader's trading activity. 
<br><br>
```{r message=FALSE, warning=FALSE, include=FALSE}
#Import Packages
library(lubridate)
library(dplyr)
library(stringi)
library(RSQLite)             
library(mongolite)
library(ggplot2)
library(quantmod)
library(PerformanceAnalytics)
library(tidyquant)
library(plotrix)
library(scales)
library(dygraphs)
library(timetk)

```

```{r echo=FALSE, message=TRUE, warning=TRUE}
#Set up directory and load Config and Params
#Args = c("C:/Users/user/Documents/BigData_in_Q.fin/Coursework/Coursework1/MuideenAbubakar/3.CourseworkThree", "script.config", "script.params")

Args <- commandArgs(TRUE)

setwd(Args[1])

#getwd()

# Source config
source(paste0("./Config/", Args[2]))

# Source params
source(paste0("./Config/", Args[3]))

#Set up connection with MongoDB and SQL
conMongo <- mongo(collection = "CourseworkTwo", db = "Equity", url = "mongodb://localhost",
                  verbose = FALSE, options = ssl_options())

conSql <- dbConnect(RSQLite::SQLite(), Config$Directories$SQLDataBase)
```

```{r echo=FALSE, message=TRUE, warning=TRUE}

#Trade Allocations 
Database <- conMongo$find()
SelectedTraderPositions <- Database[Database$Trader == params$TraderID, ]
Allocation <- SelectedTraderPositions[grep(params$TradeDate, SelectedTraderPositions$DateTime), ]

```

### Trade Allocation
```{r echo=FALSE, message=FALSE, warning=FALSE}

#Remodify the Allocation table by reducing it to the most relevant columns 
RelevantCols <- c("Symbol", "Notional", "Quantity")
Allocation_1 <- Allocation[RelevantCols]

Allocation_1 <- arrange(Allocation_1, Symbol) #sort the Symbols alphabetically

#Aggregates the Notional and Quantity based on Symbol
Allocation_2 <- aggregate(. ~ Symbol, data = Allocation_1, FUN = sum)

#Print end of day Allocation
Allocation_2

```

### Portfolio size (USD)
```{r echo=FALSE, message=FALSE, warning=FALSE}
#Compute the marked-to-market portfolio size (based on current prices)
#Get latest price data from Yahoo Finance

#Some companies have changed their tickers, so change the Symbols to match the ticker as quoted on Yahoo Finance
Allocation_2$Symbol[Allocation_2$Symbol == "SYMC"] <- "SYMC.VI" 
Allocation_2$Symbol[Allocation_2$Symbol == "BRK.B"] <- "BRK-B"
Allocation_2$Symbol[Allocation_2$Symbol == "BHGE"] <- "BKR"
Allocation_2$Symbol[Allocation_2$Symbol == "HRS"] <- "HRS.DU"

CurrentPrice <- getQuote(Allocation_2$Symbol, what=yahooQF("Last Trade (Price Only)")) 

Allocation_2$CurrentPrice <- CurrentPrice$Last

Portfolio_Size <- sum(Allocation_2$Quantity * Allocation_2$CurrentPrice)

label_comma()(Portfolio_Size)

```

### Return Analysis {.tabset .tabset-fade .tabset-pills}

#### Return to Date (%)
```{r echo=FALSE, message=FALSE, warning=FALSE}

#Calculate Portfolio Performance
#The performance of the portfolio is assessed on four different metrics;

# a.Return-to-Date (Nov-12 portfolio value vs the market value of the portfolio using marked-to-market prices) 
#Compute the average unit price
Allocation_2$UnitPrice <- Allocation_2$Notional/Allocation_2$Quantity

#Compute the return per stock based on current market price
Allocation_2$Return <- ((Allocation_2$CurrentPrice/Allocation_2$UnitPrice)-1)*100

#Compute the weight of each stock relative to the portfolio size
Allocation_2$Weight <- (Allocation_2$Notional/Portfolio_Size)

#Compute the weighted return for each stock
Allocation_2$WeightedReturn <- Allocation_2$Return*Allocation_2$Weight

#Compute the overall portfolio weighted return to date
ReturnToDate <- sum(Allocation_2$WeightedReturn)

round(ReturnToDate, 2)
```

#### Since Inception (%)
```{r echo=FALSE, message=TRUE, warning=TRUE}

# b. Return from inception (i.e. compare the current portfolio value to what it was when it started in Jan-06-20)

# Get the portfolio allocation at inception
AllocInception <- SelectedTraderPositions[grep(params$InceptionDate, SelectedTraderPositions$DateTime), ]
AllocInception <- AllocInception[, c("Symbol", "Quantity", "Notional")]

#Aggregate based on Quantity and Notional
Agg_AllocInception <- aggregate(. ~ Symbol, data = AllocInception, FUN = sum)

SinceInception <- (sum(Allocation_2$Notional)/sum(Agg_AllocInception$Notional)-1)*100

round(SinceInception,2)
```

#### 1-Day Return (%)
```{r echo=FALSE, message=TRUE, warning=TRUE}
# c. 1-day return (which compares the value of the portfolio on Nov-12 to the value on Nov-11)

AllocDay11 <- SelectedTraderPositions[grep(as.Date(params$TradeDate)-1, SelectedTraderPositions$DateTime), ]
AllocDay11 <- AllocDay11[, c("Symbol", "Quantity", "Notional")]

#Aggregate based on Quantity and Notional
Agg_AllocDay11 <- aggregate(. ~ Symbol, data = AllocDay11, FUN = sum)

Day12Return <- (sum(Allocation_2$Notional)/sum(Agg_AllocDay11$Notional)-1)*100

round(Day12Return, 2)
```

#### Alpha Return (%)
```{r echo=FALSE, message=FALSE, warning=FALSE}
# d. Alpha return, using the S&P 500 as benchmark

#Get the S&P Index level as at params$TradeDate
GSPC <- getSymbols("^GSPC", from = params$TradeDate, to = as.Date(params$TradeDate)+1, warnings = FALSE, auto.assign = FALSE)
SP500_1 <- head(GSPC)
SP500_1 <- SP500_1$GSPC.Adjusted
SP500_1 <- as.numeric(SP500_1)

SP500_Current <- getQuote("^GSPC", what=yahooQF("Last Trade (Price Only)")) 
SP500_Current <- SP500_Current$Last

Rb <- as.numeric(((SP500_Current/SP500_1)-1)*100)

Alpha = ReturnToDate - Rb
round(Alpha, 2)

#Risk-free rate (US 10-yr Treasury)
#Get the risk-free rate (US 10-yr Treasury yield) from Yahoo Finance
Rf <- getQuote("^TNX", what=yahooQF("Last Trade (Price Only)")) 
Rf <- Rf$Last
```

### Portfolio Risk Metrics {.tabset .tabset-fade .tabset-pills}

#### Standard Deviation
```{r echo=FALSE, message=FALSE, warning=FALSE}
StandardDev <- StdDev(Allocation_2$WeightedReturn)
as.numeric(round(StandardDev, 2))
```

#### Sharpe Ratio
```{r echo=FALSE, message=FALSE, warning=FALSE}
SharpeRatio <- (ReturnToDate - Rf)/StandardDev
as.numeric(round(SharpeRatio, 2))
```

#### Tracking Error
```{r echo=FALSE, message=FALSE, warning=FALSE}
TrackingErr <- StdDev(Allocation_2$WeightedReturn - Rb)^0.5
as.numeric(round(TrackingErr, 2))
```

#### Information Ratio
```{r echo=FALSE, message=FALSE, warning=FALSE}
InformationRatio <- (ReturnToDate-Rb)/TrackingErr
as.numeric(round(InformationRatio, 2))
```

### Top Holdings {.tabset .tabset-fade .tabset-pills}

#### Table
```{r echo=FALSE, message=FALSE, warning=FALSE}
#Sort Allocation_2 in descending order by Weight
Desc_Allocation_2 <- Allocation_2[order(-Allocation_2$Weight),]

#Convert the weights to %
Desc_Allocation_2$Weight <- round(Desc_Allocation_2$Weight *100,2)

#Include only Symbols and the weights
TopHoldings <- Desc_Allocation_2[, c("Symbol", "Weight")]

#Reorder the row numberings
rownames(TopHoldings) <- 1:nrow(TopHoldings)

TopTenHoldings <- head(TopHoldings, 10)

TopTenHoldings
```

#### Chart
```{r echo=FALSE, message=FALSE, warning=FALSE}

TopTenHoldingsPie <- pie3D(TopTenHoldings$Weight, border = "white", labels = TopTenHoldings$Symbol, labelcex = 0.75, explode = 0.15, shade = 0.3)

```

### Historical Price Trend {.tabset .tabset-fade .tabset-pills}

#### Relative stock performance
```{r echo=FALSE, message=FALSE, warning=FALSE}
Tickers = c(TopTenHoldings$Symbol)
stocks <- tq_get(Tickers, from = params$InceptionDate)

stocks %>% 
  dplyr::select(symbol, date, adjusted) %>% 
  tidyr::spread(key = symbol, value = adjusted) %>% 
  timetk::tk_xts() %>% 
  dygraph() %>%
  dyRebase(value = 100) %>% 
  dyRangeSelector()

```